Longest Common Extensions via Fingerprinting

### 2011-11-23 article/article.tex
m

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Average Case vs.\ Worst Case\label{sec:improved-avg}}
The first traversal in the query algorithm guarantees $O(1)$ average case performance. Without it the average case query time would be $O(k)$. However, the worst case bound would remain $O(kn^{1/k})$. Thus, for a better practical worst-case performance we could omit the first traversal entirely. We have extensively experimented with both variants and we found that in nearly all scenarios the first traversal improved the overall performance. In the cases where performance was not improved the first traversal only degraded the performance slightly. We therefore focus exclusively on the two traversal variant in the remainder of the paper.

@@

We have tested the algorithms on different kinds of strings:
\begin{description}
\item[Average case strings] These strings have many small LCE values, such that the average LCE value over all $n^2$ query pairs is less than one. We use results on these strings as an indication average case query times over all input pairs $(i,j)$ in cases where most or all LCE values are small on expected input strings. We construct these strings by choosing each character uniformly at random from an alphabet of size 10
\item[Worst case strings] These strings have many large LCE values, such that the average LCE value over all $n^2$ query pairs is $n/2$. We use results on these strings as an indication of worst case query times, since the query times for all tested algorithms are asymptotically at their worst when the LCE value is large. We construct these strings with an alphabet size of one.
\item[Medium LCE value strings] These strings have an average LCE value over all $n^2$ query pairs of $n/2r$, where $r=0.73n^{0.42}$. These strings where designed to show that \fprint\ can be faster than both \proc{DirectComp} and \proc{LcpRmq} on some inputs between the average case and worst case. The strings consist of repeating substrings of $r$ unique characters.
%The value of $r$ is a power regression over $(r,n) = (5,100)$, $(15,1.000)$, $(35,10.000)$ and $(100,100.000)$, where each of the values of $n$ were chosen such that \fprintk\ was faster than both \proc{DirectComp} and \proc{LcpRmq} on a plot with the given constant value of $r$. 
\end{description}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Average Case vs.\ Worst Case\label{sec:improved-avg}}
The first traversal in the query algorithm guarantees $O(1)$ average case performance. Without it, i.e.\ if the query started with $\ell=k-1$ and omitted step one, the average case query time would be $O(k)$. However, the worst case bound would remain $O(kn^{1/k})$. Thus, for a better practical worst-case performance we could omit the first traversal entirely. We have extensively experimented with both variants and we found that in nearly all scenarios the first traversal improved the overall performance. In the cases where performance was not improved the first traversal only degraded the performance slightly. We therefore focus exclusively on the two traversal variant in the remainder of the paper.

@@

We have tested the algorithms on different kinds of strings:
\begin{description}
\item[Average case strings] These strings have many small LCE values, such that the average LCE value over all $n^2$ query pairs is less than one. We use results on these strings as an indication average case query times over all input pairs $(i,j)$ in cases where most or all LCE values are small on expected input strings. We construct these strings by choosing each character uniformly at random from an alphabet of size 10
\item[Worst case strings] These strings have many large LCE values, such that the average LCE value over all $n^2$ query pairs is $n/2$. We use results on these strings as an indication of worst case query times, since the query times for all tested algorithms are asymptotically at their worst when the LCE value is large. We construct these strings with an alphabet size of one.
\item[Medium LCE value strings] These strings have an average LCE value over all $n^2$ query pairs of $n/2r$, where $r=0.73n^{0.42}$. These strings where designed to show that \fprint\ can be faster than both \proc{DirectComp} and \proc{LcpRmq} on some inputs between the average case and worst case. The strings consist of repeating substrings of $r$ unique characters.
The value of $r$ is a power regression over $(r,n) = (5,100)$, $(15,1.000)$, $(35,10.000)$ and $(100,100.000)$, where each of the values of $n$ were chosen such that \fprintk\ was faster than both \proc{DirectComp} and \proc{LcpRmq} on a plot with the given constant value of $r$. 
\end{description}
